Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-03-12 eswc-2012/phdsymp.tex
more contributions
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@177 43ef1190-90fd-4dd7-a769-d0121f02b80e

\item To assist optimization, enable endpoint service descriptions to
  expose:
\begin{itemize}
\item performance characteristics,
\item statistical digests of data that are optimized with respect to
  size and query performance.
\end{itemize}
\end{itemize}

@@

Ultimately, this approach may be of great value to new users of SPARQL
engines, as it can point out key differences between engines and
therefore help users identify aspects that they should investigate
with respect to their own expected uses. By normalizing weights
between features, we may also attempt to advice those who do not know
anything about their expected usage. Similarly, it may of great use to
developers as it would quantify any adverse effects a modification may
have.

>>>>

\item To assist optimization, enable endpoint service descriptions to
  expose:
\begin{itemize}
\item performance characteristics,
\item statistical digests of data that are optimized with respect to
  size and query performance.
\end{itemize}
\item SPARQL engine developers can use the benchmark to reliably
  quantify unexpected adverse effects from a given modification.
\item New SPARQL engine users can identify key differences between
  different engines, and therefore be able to more wisely choose
  engine to use.
\end{itemize}

@@
